### 2013-10-01 Rcode/test.mix.Rmd
updated ash to use normalmix methods rather in mix.R to compute posterior mean, PositiveProb, NegativeProb etc
added computing of posterior mean for uniform prior; however it is not yet numerically stable when the prior and the likelihood disagree

@@

```{r}

temp2 = unimix(c(0.5,0.5),c(-3,3),c(-1,4))
plot_dens(temp2)

@@

>>>>

```{r}
############## HELPER FUNCTIONS #################################################
#OUTPUT: k by n matrix of normal densities
matdnorm = function (x, mu, sigma, log=FALSE) 
{
  k=length(mu)
  n=length(x)
  d = matrix(rep(x,rep(k,n)),nrow=k)
  return(matrix(dnorm(d, mu, sigma, log),nrow=k))
}
```

@@

```{r}
temp2 = unimix(c(0.5,0.5),c(-3,3),c(-1,4))
plot_dens(temp2)

@@

```{r}
  comp_postmean(temp2, c(1,2,3), c(10,10,10))
  comp_postmean(temp2, c(1,2,3), c(0.1,0.1,0.1))
```
